### 2019-03-05 README.Rmd
update plot and readme

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(deeptriangle)
library(tidyverse)
library(keras)
```

@@

## Reproducing experiments

@@

The following lines of code will instantiate and fit the model for each line of business then combine the forecasts in a data frame:

```{r, message = FALSE, cache = TRUE}
library(deeptriangle)
library(tidyverse)
library(keras)

# set seed for reproducibility
use_session_with_seed(2018)

data <- dt_data_prep(insurance::schedule_p, dt_group_codes)

lobs <- c("workers_compensation", "commercial_auto",
          "private_passenger_auto", "other_liability")

predictions <- lobs %>%
  map(
    function(x) {
      # clear session and instantiate model
      k_clear_session()
      model <- dt_model()

      c(training_data, validation_data, full_training_data) %<-%
        dt_train_validation_split(data[[x]])

      message("Training - ", x)

      # determine number of epochs
      epochs_to_train <- dt_optimize_epochs(
        model, training_data, validation_data
      )

      # clear session and reinstantiate model
      k_clear_session()
      model <- dt_model()

      # fit model to all training data
      history <- model %>%
        fit(x = full_training_data$x,
            y = full_training_data$y,
            batch_size = 128,
            epochs = epochs_to_train,
            verbose = 0)
      dt_compute_predictions(model, data[[x]])
    }) %>%
  bind_rows()
```

We can then compute performance metrics...

```{r}
model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  gather(metric, value, mape, rmspe)
```

and tabulate the results:

```{r}
dt_tabulate_metrics(model_results, metric = "mape") %>%
  knitr::kable(booktabs = "T", digits = 3)
```

```{r}
dt_tabulate_metrics(model_results, metric = "rmspe") %>%
  knitr::kable(booktabs = "T", digits = 3)
```

To create actual vs. predicted plots, use the `dt_plot_predictions()` function.

```{r, out.width = "60%"}
dt_plot_predictions(predictions, "337", "workers_compensation",
                    "paid_loss")
```

```{r, out.width = "60%"}
dt_plot_predictions(predictions, "337", "workers_compensation",
                    "claims_outstanding")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(deeptriangle)
library(tidyverse)
```

@@

## Experiments

@@

The experiments can be found in `analysis/main.R`. It is recommended that you use a GPU since many instances of the models are fit.

For convenience, we provide a `predictions.feather` file in the release.

```{r, message = FALSE}
predictions <- feather::read_feather("output/predictions.feather")

model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(read_csv("analysis/automl_results.csv")) %>%
  gather(metric, value, mape, rmspe)

dt_tabulate_metrics(model_results, metric = "mape") %>%
  knitr::kable(booktabs = "T", digits = 3)
```

To create actual vs. predicted plots, use the `dt_plot_predictions()` function. Here are successful and unsuccessful examples of the model's forecasting attempts.

Company 1767 commercial auto.

```{r, echo = FALSE, message = FALSE, out.width = "80%"}
library(cowplot)

p1 <- dt_plot_predictions(predictions, "1767", "commercial_auto", "paid_loss") + xlab("")
p2 <- dt_plot_predictions(predictions, "1767", "commercial_auto", "claims_outstanding")
p12 <- plot_grid(
  p1 + theme(legend.position = "none"),
  p2 + theme(legend.position = "none"),
  align = "v",
  ncol = 1
)
legend <- get_legend(p1)
plot_grid(p12, legend, rel_widths = c(1, 0.2), nrow = 1)
```

Company 337 workers' compensation.

```{r, echo = FALSE, message = FALSE, out.width = "80%"}
library(cowplot)

p1 <- dt_plot_predictions(predictions, "337", "workers_compensation", "paid_loss") + xlab("")
p2 <- dt_plot_predictions(predictions, "337", "workers_compensation", "claims_outstanding")
p12 <- plot_grid(
  p1 + theme(legend.position = "none"),
  p2 + theme(legend.position = "none"),
  align = "v",
  ncol = 1
)
legend <- get_legend(p1)
plot_grid(p12, legend, rel_widths = c(1, 0.2), nrow = 1)
```

## Testing different architectures

If you would like to try out different architectures or hyperparameters, you can do so by providing a function that returns a keras model. See the source code of `dt_model()` for a template.

For more details on the **keras** R package, visit [https://keras.rstudio.com/](https://keras.rstudio.com/).
